Qualifying Report

### 2018-05-14 QualifyingReport/QualifyingReport.tex
Updated Qualifying Report - 14-05-2018

	\subsection{Literature Review - April 2018 to July 2018}
	A literature review was carried out from several perspectives in order to understand both an applied and theoretical perspective. Thus a search for papers was conducted in both the psychology and computer science domains, as well as papers which intersected these areas and were relevant to this particular problem.
	\newline
	SEARCH - ProQuest (PsychArticles) - Search Terms (Language AND Decline AND DEMENTIA) - 1484 Results
	SEARCH - ProQuest (PsychArticles) - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 486 Results
	SEARCH - Web Of Science - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 151 Results
	SEARCH - Web of Science - Search Terms (Language AND Decline AND DEMENTIA) - 1207 Results
	SEARCH - Scopus - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 91 Results 
	SEARCH - Scopus - Search Terms (Languge AND DEMENTIA AND Decline) - 791 Results
	\newline
	Studies that met the following criteria were included: articles that addressed the association between language and all forms of dementia. Studies with one or more of the following characteristics were not included in this literature review: articles and dissertations that did not meet the selected inclusion in different databases and those that were not available in it's original form.

@@

>>>>

	\subsection{Literature Review - April 2018 to July 2018}
	A literature review was carried out from several perspectives in order to understand both an applied and theoretical perspective. Thus a search for papers was conducted in both the psychology and computer science domains, as well as papers which intersected these areas and were relevant to this particular problem.
	\newline
	SEARCH - ProQuest (PsychArticles) - Search Terms (Language AND Decline AND DEMENTIA) - 1484 Results \newline
	SEARCH - ProQuest (PsychArticles) - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 486 Results \newline
	SEARCH - Web Of Science - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 151 Results\newline
	SEARCH - Web of Science - Search Terms (Language AND Decline AND DEMENTIA) - 1207 Results\newline
	SEARCH - Scopus - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 91 Results\newline 
	SEARCH - Scopus - Search Terms (Languge AND DEMENTIA AND Decline) - 791 Results
	\newline
	Studies that met the following criteria were included: articles that addressed the association between language and all forms of dementia. Studies with one or more of the following characteristics were not included in this literature review: articles and dissertations that did not meet the selected inclusion in different databases and those that were not available in it's original form.

@@

	\appendix
	\section{Title of Appendix A}

	Text of Appendix A is Here

	\section{Title of Appendix B}

	Text of Appendix B is Here
